\textbf{Towards File System integrity verification in BTRFS}

### 2019-07-30 paper.tex
Reorder companies

\section{File System Architecture}
BTRFS\cite{BTRFS} is a general purpose File System for the Linux Operating
system that was first introduced in 2009. BTRFS is based on a copy-on-write
\footnote{\href{https://en.wikipedia.org/wiki/Copy-on-write\#In\_computer\_storage}
{https://en.wikipedia.org/wiki/Copy-on-write\#In\_computer\_storage}} capable
B-tree\cite{rodeh} data-structure. The main features of BTRFS are
copy-on-write, File System level snapshots, subvolumes, data and meta-data
checksums, transparent compression and multi-device storage pools. BTRFS is
mainly developed by Facebook, Fujitsu, SUSE and
Oracle\footnote{\href{https://btrfs.wiki.kernel.org/index.php/Contributors}
{https://btrfs.wiki.kernel.org/index.php/Contributors}} but has had
contributions from other companies as well in the past.

>>>>

\section{File System Architecture}
BTRFS\cite{BTRFS} is a general purpose File System for the Linux Operating
system that was first introduced in 2009. BTRFS is based on a copy-on-write
\footnote{\href{https://en.wikipedia.org/wiki/Copy-on-write\#In\_computer\_storage}
{https://en.wikipedia.org/wiki/Copy-on-write\#In\_computer\_storage}} capable
B-tree\cite{rodeh} data-structure. The main features of BTRFS are
copy-on-write, File System level snapshots, subvolumes, data and meta-data
checksums, transparent compression and multi-device storage pools. BTRFS is
mainly developed by SUSE, Facebook, Oracle and Fujitsu
\footnote{\href{https://btrfs.wiki.kernel.org/index.php/Contributors}
{https://btrfs.wiki.kernel.org/index.php/Contributors}} but has had
contributions from other companies as well in the past.
